Relationships in the extremes and their influence on competition and coexistence

### 2021-07-21 paper/Paper.Rnw
adding refs per Dan request

%Old version, prior to my edits: Central to ecology is the maintenance of biodiversity in competitive ecosystems. Populations subject to strong
%competitive pressure may succumb to competitive exclusion - an idea which postulates if species within the same
%trophic level and similar niches exist, one will eventually outcompete the other (Hardin, 1960). Mediation of
%competitive pressure and exclusion allow for species to stably coexist. The criteria for coexistence and competitive
%exclusion can be broken down into contributing mechanisms provided by modern coexistence theory, a framework
%which seeks to assess and quantify mechanisms that result in coexisting species and thus the maintenance of
%biodiversity (Chesson, 1994).
%Now the new, edited version, with some additional changes requested, to be made by Jasmin, please:
The maintenance of biodiversity in competitive ecosystems is a research topic at the absolute core of modern ecology.
%***DAN: Jasmin, add a few classic references. See the first sentence of Ellner et al 2019, read the abstracts of those papers
%(more than the abstracts if you want), and consider using them as references here.
The competitive exclusion principle, covered, for instance, in most or all introductory ecology courses and texts, states 
that two species competing for the same limiting resource cannot coexist at constant densities - one will outcompete 
the other and drive it extinction \citep{Hardin_1960}.
Modern coexistence theory [MCT; \cite{Chesson_1994,Chesson_2000,Barabas_2018}] is a 
framework for understanding how stable species coexistence 
nevertheless occurs, and biodiversity in maintained, in real ecosystems, through stabilizing mechanisms and niche 
differentiation, in spite of the conclusions drawn for idealized scenarios by the competitive exclusion principle. 
MCT breaks down coexistence into the contributions of various mechanisms, with name such as `relative nonlinearity
in competition' and `storage effects' \citep{Chesson_1994} which will be familiar to many readers. The MCT has been
applied to quite a few empirical systems, including annual plants \citep{Angert_2009}, Y and Z, 
%***DAN: Jasmin, fill in Y and Y with names of systems, and accompanying reference(s), 
%in a similar way to how I filled in the Angert example.
%Please also read the abstract of the Angert reference to make sure it is appropriate to cite it in this way (and so that
%you become aware of that reference). One place to look for more references to put in for Y and Z is the top of the 
%right column on the first page of the Barabas review (Ecol Monogr, 2018).
even though it is mathematically complex in the eyes
of most ecologists (but see \cite{Ellner_2016,Ellner_2019} for efforts to make it more readily applied).
%***DAN: Jasmin, note the differences carefully, please, between your version (commented, above) and the edits I've 
%made. It's the same in main structure, making all the same points. It's just a bit more fleshed out. One of the purposes
%of an Intro is to link the reader to the appropriate background lit. You need a fair number of references and a little
%more detail than you previously gave to do that.

@@

considered in ecology and related areas (but see REFS), 

>>>>

%Old version, prior to my edits: Central to ecology is the maintenance of biodiversity in competitive ecosystems. Populations subject to strong
%competitive pressure may succumb to competitive exclusion - an idea which postulates if species within the same
%trophic level and similar niches exist, one will eventually outcompete the other (Hardin, 1960). Mediation of
%competitive pressure and exclusion allow for species to stably coexist. The criteria for coexistence and competitive
%exclusion can be broken down into contributing mechanisms provided by modern coexistence theory, a framework
%which seeks to assess and quantify mechanisms that result in coexisting species and thus the maintenance of
%biodiversity (Chesson, 1994).
%Now the new, edited version, with some additional changes requested, to be made by Jasmin, please:
The maintenance of biodiversity in competitive ecosystems is a research topic at the absolute core of modern ecology (\citep{MacArthur_1958, Hutchinson_1961, Schmida_1984}.
%***DAN: Jasmin, add a few classic references. See the first sentence of Ellner et al 2019, read the abstracts of those papers
%(more than the abstracts if you want), and consider using them as references here.
The competitive exclusion principle, covered, for instance, in most or all introductory ecology courses and texts, states 
that two species competing for the same limiting resource cannot coexist at constant densities - one will outcompete 
the other and drive it extinction \citep{Hardin_1960}.
Modern coexistence theory [MCT; \cite{Chesson_1994,Chesson_2000,Barabas_2018}] is a 
framework for understanding how stable species coexistence 
nevertheless occurs, and biodiversity in maintained, in real ecosystems, through stabilizing mechanisms and niche 
differentiation, in spite of the conclusions drawn for idealized scenarios by the competitive exclusion principle. 
MCT breaks down coexistence into the contributions of various mechanisms, with name such as `relative nonlinearity
in competition' and `storage effects' \citep{Chesson_1994} which will be familiar to many readers. The MCT has been
applied to quite a few empirical systems, including annual plants \citep{Angert_2009, Hallett_2019}, perennial plants \citep{Adler_2010}, tropical trees \citep{Usinowicz_2012}, plankton \citep{Narawani_2013, Caceres_1997}, and corals \citep{}. 
%***DAN: Jasmin, fill in Y and Y with names of systems, and accompanying reference(s), 
%in a similar way to how I filled in the Angert example.
%Please also read the abstract of the Angert reference to make sure it is appropriate to cite it in this way (and so that
%you become aware of that reference). One place to look for more references to put in for Y and Z is the top of the 
%right column on the first page of the Barabas review (Ecol Monogr, 2018).
even though it is mathematically complex in the eyes
of most ecologists (but see \cite{Ellner_2016,Ellner_2019} for efforts to make it more readily applied).
%***DAN: Jasmin, note the differences carefully, please, between your version (commented, above) and the edits I've 
%made. It's the same in main structure, making all the same points. It's just a bit more fleshed out. One of the purposes
%of an Intro is to link the reader to the appropriate background lit. You need a fair number of references and a little
%more detail than you previously gave to do that.

@@

considered in ecology and related areas (but see \citep{Anderson_2018, deValpine_2014, Popovic_2019}), 
